% ___      _ _   _      _ _          _   _          
%|_ _|_ _ (_) |_(_)__ _| (_)___ __ _| |_(_)___ _ _  
% | || ' \| |  _| / _` | | (_-</ _` |  _| / _ \ ' \ 
%|___|_||_|_|\__|_\__,_|_|_/__/\__,_|\__|_\___/_||_|                          

\documentclass[a4paper, 12pt,oneside]{article}

% pour l'inclusion de figures en eps,pdf,jpg,....
\usepackage{graphicx}
% Pour que les figures soit cote à cote
\usepackage{subfigure}
% Pour que la figure soit à coté du texte
\usepackage{wrapfig}

%pour que la figure soit à l'endroit souhaiter [H]
\usepackage{float} 

\usepackage{multirow}

\usepackage{ upgreek }

\usepackage{amssymb}

\usepackage[usenames,dvipsnames]{color}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{tcolorbox}
\usepackage{mdframed}


%Marges. Désactiver pour utiliser les valeurs LaTeX par défaut
%\usepackage[top=2.5cm, bottom=2cm, left=2cm, right=2cm, showframe]{geometry}
\usepackage[top=2.5cm, bottom=2cm, left=2cm, right=2cm]{geometry}

% quelques symboles mathematiques en plus
\usepackage{amsmath}
\usepackage{physics}
\usepackage{amsfonts}

% on peut ecrire directement les charactères avec l'accent
\usepackage[T1]{fontenc}

% a utiliser sur Linux/Windows
%\usepackage[latin1]{inputenc}

% a utiliser avec UTF8
\usepackage[utf8]{inputenc}
%Très utiles pour les groupes mixtes mac/PC. Un fichier texte enregistré sous codage UTF-8 est lisible dans les deux environnement.
%Plus de problème de caractères accentués et spéciaux qui ne s'affichent pas

% pour l'inclusion de liens dans le document (pdflatex)
\usepackage[colorlinks,bookmarks=false,linkcolor=black,urlcolor=blue, citecolor=black]{hyperref}

%Pour l'utilisation plus simple des unités et fractions
\usepackage{units}

%Pour utiliser du time new roman... Comenter pour utiliser du ComputerModern
\usepackage{mathptmx}

%Pour du code non interprété
\usepackage{listings}
\usepackage{verbatim}
\usepackage{verbdef}
\usepackage{lipsum}
\usepackage{mathtools}

\usepackage{esvect}

\def \be {\begin{equation}}
\def \ee {\end{equation}}

%Pour changer la taille des titres de section et subsection. Ajoutez manuellement les autres styles si besoin.
\makeatletter
\renewcommand{\section}{\@startsection {section}{1}{\z@}%
             {-3.5ex \@plus -1ex \@minus -.2ex}%
             {2.3ex \@plus.2ex}%
             {\normalfont\normalsize\bfseries}}
\makeatother

\makeatletter
\renewcommand{\subsection}{\@startsection {subsection}{1}{\z@}%
             {-3.5ex \@plus -1ex \@minus -.2ex}%
             {2.3ex \@plus.2ex}%
             {\normalfont\normalsize\bfseries}}
\makeatother

% Prepare code listing package
\definecolor{codegreen}{rgb}{0,0.6,0.2}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.8,0,0.8}
\definecolor{backcolour}{rgb}{0.92,0.92,0.95}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

% ___                             _   
%|   \ ___  __ _  _ _ __  ___ _ _| |_ 
%| |) / _ \/ _| || | '  \/ -_) ' \  _|
%|___/\___/\__|\_,_|_|_|_\___|_||_\__|
                                     

\begin{document}
\title{MAT library - Documentation}
\date{\normalsize{\today}}
\author{Rotunno Noah}
\maketitle

\tableofcontents
\newpage

\section{Introduction}
A mathematical library that implement mathematical classes and functions. The header files of the library has to be included in the "include" folder of your application. No dynamicly link library (dll) or static library (lib) are required. The file \textit{Math.hpp} has to be included:

\begin{lstlisting}[language=C++]
#include <Math.hpp>
\end{lstlisting}

Some type definitions are already implemented. To choose if you want to use these type definitions, the macro \textit{MAT\textunderscore TYPEDEF}
 has to be defined to 1  or 0 to respectively use the type definitions or not. This has to be done \textbf{before} including \textit{Math.hpp}. Example :

\begin{lstlisting}[language=C++]
#define MAT_TYPEDEF 1 /* use 0 to not use the type definitions */
#include <Math.hpp>
\end{lstlisting}

\section{Types}
This section contain the types of MatObject, the type of content allowed and the function associated with them,
\input{Text/Type.tex}

\section{Classes}
This section contain the documentation and the prototype of the different classes. There is also the different functions associated to the classes. Each method and function has de brief explanation and the parameters and template parameters are explained. There is also a brief explanation on the return and if the method or function has some warning to consider.

\input{Text/MatObject.tex}

\input{Text/BaseVector.tex} 

\subsection{BaseVector functions}
\input{Text/BaseVectorFunction.tex}

\input{Text/Vector.tex}

\subsection{Vector functions}
\input{Text/VectorFunction.tex}

\input{Text/Matrix.tex}

\subsection{Matrix functions}
\input{Text/MatrixFunction.tex}

\input{Text/Complex.tex}

\subsection{Complex functions}
\input{Text/ComplexFunction.tex}

\input{Text/Quaternion.tex}

\subsection{Quaternion functions}
\input{Text/QuaternionFunction.tex}





\end{document}
